---
title: "Assignment_1"
author: "Pierre-Olivier Couture"
format: html
editor: visual
---

## Comment

This is all my code and explanation for Assignment 1 in PSYR 6003 Fundamental of Applied Stats (Winter).

## Question 1: Install all required packages and load in the data set

```{r}
#| label: Installing and loading in all packages
# This is the code for installing all the libraries I require for this code and then once it is installed, I call it back (make sure R knows to use it) 

installed.packages("tidyverse")
library(tidyverse)
library(readr)
library(haven)

```

```{r}
#| label: Load in the Data
# This is the code for loading in the "avengers.csv' file from GitHub to my RStudio. 

avengers <- read_csv("avengers.csv")

```

## Question 2: Creating a new variable called 'CombatEffectiveness'

```{r}
#| label: Creating CombatEffectiveness
# This is the code I used for to sum the columns of speed, agility, strength
# and willpower into a new variable called 'CombatEffectiveness.' While doing 
# this I will also only include complete, clean cases and not count incomplete
# responses. Directly below it I will print the results to make sure the code 
# worked correctly.

avengers <- avengers %>%
  mutate(CombatEffectiveness = rowSums(across(c(speed, agility, strength, willpower)), na.rm = TRUE))

print(avengers)

```

## Question 3a) Making an SPSS copy

```{r}
#| label: SPSS copy
# This is the code I used to make a copy of the dataset in an SPSS format but it
# will only include the avengers who did not have a superpower and have died. 

avengers_SPSS <- avengers %>%
  filter(superpower == FALSE, died == "Yes")

# The following code will save the code for to an SPSS format

write_sav(avengers_SPSS, "avengers_no_super_dead")

```

## Question 3b) Making a csv copy

```{r}
#| label: CSV copy
# This is the code I used to make a copy of the dataset in a CSV format but it
# will only include the avengers who did not have a superpower and have died.

avengers_CSV <- avengers %>%
  filter(superpower == FALSE, died == "Yes")

# The following code will save the code for to a CSV format

write_csv(avengers_CSV, "avengers_no_super_dead.csv")

```

## Question 3c) Summarize the dataset

```{r}
#| label: Summarizing the data
# This is the code I will use to understand the properties of combat 
# effectiveness, kills, and injuries. This will present the mean, sd, and range
# values for those variables.

# This is the code for 'CombatEffectiveness' 

summarise(avengers,avg_CombatEffectiveness = mean(CombatEffectiveness,na.rm=TRUE))
summarise(avengers,sd_CombatEffectiveness = sd(CombatEffectiveness,na.rm=TRUE))
range(avengers$CombatEffectiveness, na.rm = TRUE)

# This is the code for 'kills'

summarise(avengers,avg_kills = mean(kills,na.rm=TRUE))
summarise(avengers,sd_kills = sd(kills,na.rm=TRUE))
range(avengers$kills, na.rm = TRUE)

# This is the code for 'injuries'

summarise(avengers,avg_injuries = mean(injuries,na.rm=TRUE))
summarise(avengers,sd_injuries = sd(injuries,na.rm=TRUE))
range(avengers$injuries, na.rm = TRUE)

```

The `echo: false` option disables the printing of code (only output is displayed).
