---
title: "Assignment_1"
author: "Pierre-Olivier Couture"
format: html
editor: visual
---

## Comment

This is all my code and explanation for Assignment 1 in PSYR 6003 Fundamental of Applied Stats (Winter).

## Question 1: Install all required packages and load in the data set

```{r}
#| label: Installing and loading in all packages
# This is the code for installing all the libraries I require for this code and then once it is installed, I call it back (make sure R knows to use it) 

installed.packages("tidyverse")
library(tidyverse)
library(readr)
library(haven)

```

```{r}
#| label: Load in the Data
# This is the code for loading in the "avengers.csv' file from GitHub to my RStudio. 

avengers <- read_csv("avengers.csv")

```

## Question 2: Creating a new variable called 'CombatEffectiveness'

```{r}
#| label: Creating CombatEffectiveness
# This is the code I used for to sum the columns of speed, agility, strength
# and willpower into a new variable called 'CombatEffectiveness.' While doing 
# this I will also only include complete, clean cases and not count incomplete
# responses. Directly below it I will print the results to make sure the code 
# worked correctly.

avengers <- avengers %>%
  mutate(CombatEffectiveness = rowSums(across(c(speed, agility, strength, willpower)), na.rm = TRUE))

print(avengers)

```

## Question 3a) Making an SPSS copy

```{r}
#| label: SPSS copy
# This is the code I used to make a copy of the dataset in an SPSS format but it
# will only include the avengers who did not have a superpower and have died. 

avengers_SPSS <- avengers %>%
  filter(superpower == "no", died == "yes")

# The following code will save the code for to an SPSS format

write_sav(avengers_SPSS, "avengers_no_super_dead.SPSS")

```

## Question 3b) Making a csv copy

```{r}
#| label: CSV copy
# This is the code I used to make a copy of the dataset in a CSV format but it
# will only include the avengers who did not have a superpower and have died.

avengers_CSV <- avengers %>%
  filter(superpower == "no", died == "yes")

# The following code will save the code for to a CSV format

write_csv(avengers_CSV, "avengers_no_super_dead.csv")

```

## Question 3c) Summarize the dataset

```{r}
#| label: Summarizing the data for Combat Effectiveness

# This is the code I will use to understand the properties of combat 
# effectiveness, kills, and injuries. This will present the mean, sd,  # and range values for those variables.

# This is the code for 'CombatEffectiveness' 
summarise(avengers,avg_CE = mean(CombatEffectiveness,na.rm=TRUE))
summarise(avengers,sd_CE = sd(CombatEffectiveness,na.rm=TRUE))
range(avengers$CombatEffectiveness, na.rm = TRUE)
```

```{r}
#| label: Summarizing the data for kills

# This is the code for 'kills'
summarise(avengers,avg_kills = mean(kills,na.rm=TRUE))
summarise(avengers,sd_kills = sd(kills,na.rm=TRUE))
range(avengers$kills, na.rm = TRUE)
```

```{r}
#| label: Summarizing the data for injuries

# This is the code for 'injuries'
summarise(avengers,avg_injuries = mean(injuries,na.rm=TRUE))
summarise(avengers,sd_injuries = sd(injuries,na.rm=TRUE))
range(avengers$injuries, na.rm = TRUE)
```

## Question 3d) Dividing the North and South 

```{r}
#| label:  Mean/sd and range for North
# Here is the code I used to separate the data into those from the North and
# South battlefield. 

north_stats <- avengers_CSV %>%
  filter(north_south == "north") %>%
  summarise(
    mean_CombatEffectiveness = mean(CombatEffectiveness, na.rm = TRUE),
    sd_CombatEffectiveness = sd(CombatEffectiveness, na.rm = TRUE),
    min_CombatEffectiveness = min(CombatEffectiveness, na.rm = TRUE),
    max_CombatEffectiveness = max(CombatEffectiveness, na.rm = TRUE),
    
    mean_injuries = mean(injuries, na.rm = TRUE),
    sd_injuries = sd(injuries, na.rm = TRUE),
    min_injuries = min(injuries, na.rm = TRUE),
    max_injuries = max(injuries, na.rm = TRUE),
    
    mean_kills = mean(kills, na.rm = TRUE),
    sd_kills = sd(kills, na.rm = TRUE),
    min_kills = min(kills, na.rm = TRUE),
    max_kills = max(kills, na.rm = TRUE)
  )

print(north_stats)

```

```{r}
#| label:  Mean/sd and range for South
# Here is the code I used to separate the data into those from the North and
# South battlefield. 

south_stats <- avengers_CSV %>%
  filter(north_south == "south") %>%
  summarise(
    mean_CombatEffectiveness = mean(CombatEffectiveness, na.rm = TRUE),
    sd_CombatEffectiveness = sd(CombatEffectiveness, na.rm = TRUE),
    min_CombatEffectiveness = min(CombatEffectiveness, na.rm = TRUE),
    max_CombatEffectiveness = max(CombatEffectiveness, na.rm = TRUE),
    
    mean_injuries = mean(injuries, na.rm = TRUE),
    sd_injuries = sd(injuries, na.rm = TRUE),
    min_injuries = min(injuries, na.rm = TRUE),
    max_injuries = max(injuries, na.rm = TRUE),
    
    mean_kills = mean(kills, na.rm = TRUE),
    sd_kills = sd(kills, na.rm = TRUE),
    min_kills = min(kills, na.rm = TRUE),
    max_kills = max(kills, na.rm = TRUE)
  )

print(south_stats)

```

## Question 4) Efficacy and Kills

```{r}
#| label: Most effective battle field and most kills
#| eval: false
#| include: false
# This section will not run any code but is instead used to help me keep track 
# of my code better and I include the summary stats that I have calculated above 
# to make it easier for me to reference back to later when writing my report.

#########
##### NORTH STATS
#########
# mean_CombatEffectiveness = 499.7815
# sd_CombatEffectiveness = 174.0656
# min_CombatEffectiveness = 130.68
# max_CombatEffectiveness = 897.06

# mean_injuries = 4.60274
# sd_injuries = 0.6819035
# min_injuries = 2
# max_injuries = 5

# mean_kills = 1.712329
# sd_kills = 4.565813
# min_kills = 0
# max_kills = 34

#########
##### SOUTH STATS
#########
# mean_CombatEffectiveness = 491.6771
# sd_CombatEffectiveness = 189.5299
# min_CombatEffectiveness = 67.25
# max_CombatEffectiveness = 946.89

# mean_injuries = 4.428571
# sd_injuries = 0.8789123
# min_injuries = 2
# max_injuries = 5

# mean_kills = 4.75
# sd_kills = 14.9929
# min_kills = 0
# max_kills = 79

```

## Question 5) Most erroneous variables

```{r}
#| label: Most erroneous variable between combat effectiveness, kills, and injuries
# Same thing as Q4, this will not run code and will allow me to compare the 
# stats from the 3 variables. I will use the sd to determine how erroneous the 
# variables are as well as the range of values. This will not look at north vs
# south and will use it based on the total sample calculation made in Q3c.

############## STATS
#### CE
# avg = 982.1511
# sd = 10,494.71
# min / max = 67.25 / 300,000

#### Kills
# avg = 3.833744
# sd = 10.78843
# min / max = 0 / 176

#### Injuries
# avg = 3.488916
# sd = 1.262618
# min / max = 0 / 5

```













