---
title: "Assignment_1"
author: "Pierre-Olivier Couture"
format: html
editor: visual
---

## Comment

This is all my code and explanation for Assignment 1 in PSYR 6003 Fundamental of Applied Stats (Winter).

## Question 1: Begin by cloning the repo for the assignment that contains the dataset. Once you have the data, import it in any way you wish and inspect the dataset for any missing or unusual values

This is the code I will use to import the data from "https://github.com/iyakoven/PSYR6003-Assignment-1" to RStudio.

```{r}
#| label: Installing and loading in all packages
# This is the code for installing all the libraries I require for this code and then once it is installed, I call it back (make sure R knows to use it) 

installed.packages("tidyverse")
library(tidyverse)
library(readr)

```

```{r}
#| label: Load in the Data
# This is the code for loading in the "avengers.csv' file from GitHub to my RStudio. 

avengers <- read_csv("avengers.csv")

```


## Question 2: Creating a new variable called 'CombatEffectiveness'

```{r}
#| label: Creating CombatEffectiveness
# This is the code I used for to sum the columns of speed, agility, strength
# and willpower into a new variable called 'CombatEffectiveness.' While doing 
# this I will also only include complete, clean cases and not count incomplete
# responses. Directly below it I will print the results to make sure the code 
# worked correctly.

avengers <- avengers %>%
  mutate(CombatEffectiveness = rowSums(across(c(speed, agility, strength, willpower)), na.rm = TRUE))

print(avengers)

```
##

```{r}
#| label: 
```




The `echo: false` option disables the printing of code (only output is displayed).
